%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0.3in]{geometry} % Document margins

\name{Scott Harvey} % Your name
%\address{2 Head of the River \\ Smithtown, NY 11787} % Your address
\address{scott.harvey@stonybrook.edu \\ github.com/sctthrvy \\ Smithtown, NY \\ (631)~$\cdot$~624~$\cdot$~6265} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Stony Brook University, New York} \hfill {\em GPA: 3.62} \\ 
M.S. Computer Science \hfill {\em Expected May 2016}\\
B.S. Computer Science, B.S. Applied Math \& Statistics \hfill {\em Dec. 2014}
  % \smallskip \\


\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C, Python, Java, x86-64, SQL, JavaScript, SML, MATLAB \\
Tools/Other & git, Vim, make, CMake, GDB, *nix, Perforce, MySQL Workbench, Wireshark
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{SBUnix, {\em C/x86-64 Preemptive OS}}{{\em Spring 2015}}{}{}
\item Implemented COW forking, 64 bit ELF loading, ring-3 userland, timesliced prememption.
\item Developed a shell with sleep/kill/ps, standard library, read-only FS, pipes, auto-growing stack.
\end{rSubsection}

\begin{rSubsection}{File Descriptor Daemon, {\em C Networking}}{{\em Winter 2014}}{}{}
\item Designed a daemon which allows under privileged processes to obtain raw and packet sockets.
\item Created to replace setuid or NET\_CAP\_RAW on a machine intended for packet socket programming.
%\item Also supports other dangerous tasks such as opening and sending arbitrary files.
\end{rSubsection}

\begin{rSubsection}{On Demand Routing, {\em C Networking}}{{\em Fall 2014}}{}{}
\item Programmed a shortest-hop routing protocol to replace IP in static networks of unknown connectivity.
%\item Used packet sockets to discover routes and forward application payloads.
%\item Local ODR server performed the routing and multiplexed messages to apps using local sockets.
\item Used packet sockets for route discovery and forwarding; local sockets for delivering payloads to apps.
\end{rSubsection}

\begin{rSubsection}{xTCP, {\em C Networking}}{{\em Fall 2014}}{}{}
\item Implemented a reliable byte-stream transport protocol over UDP, based off TCP Reno.
\item Featured smoothed-RTT based retransmission timeout and fast retransmission.
\end{rSubsection}

\begin{rSubsection}{TravelociRaptor, {\em Java Webapp}}{{\em Spring 2014}}{}{}
\item Created a flight reservation and reverse auction webapp using JSP, SQL, and Bootstrap.
\item Designed the MySQl database to support customers, employees, and managers.
\end{rSubsection}

\begin{rSubsection}{Nachos, {\em Java OS}}{{\em Fall 2013}}{}{}
\item Worked on modules of a Java OS which ran COFF binaries using a MIPS emulator.
%\item Implemented paging and virutal memory 
\item Added virtual memory, a program loader, various syscalls, a write-back cache and a disk driver.
%\item Implemented a persistent file system, including a consistency check akin to fsck.
%\item Extended the cpu to support switchable (at boot-time) scheduling hueristics.
%\item Implemented switchable c-look, c-scan disk I/O scheduling.
%\item Loaded compiled C programs on/off disk, initializing their virtual address space.
%\item Extended the kernel and MIPS syscall interface to trap new syscalls provided to C user programs. Created mmap, munmap, yield, join, exec, read,write, exit, ...
%\item Logged stats of user threads: number of disk I/O’s, time spent in kernel mode, blocked, user mode.
\end{rSubsection}

\begin{rSubsection}{Spriter, {\em Java Application}}{{\em Fall 2012}}{}{}
\item Created a 2D drawing editor using Swing to create sequences of poses for animating game sprites.
\item Completed from an unfinished and broken starting state of 25+ classes.
%\item Saved/loaded sprites into internal XML files based on shapes drawn.
%\item Added exporting to sequential PNGs based on animation, for 2D game use.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Software Development Intern, {\em Arista Networks}}{\em Summer 2015}{}{}
%\item Added features and tests to a new agent that manages tunnel interfaces in EOS, a Linux switch OS.
\item Added features and tests to an agent that manages tunnel interfaces in EOS.
\item Worked on project to run routing protocols across GRE tunnels.
%\item Scale tested tunnels to determine rate limits to protect the CPU.
%\item Control Plane Policing of various tunneled traffic.
\end{rSubsection}

\begin{rSubsection}{Research Assistant under Prof. Scott Smolka, {\em Stony Brook University}}{\em July - Dec 2014}{}{}
\item Researched run-time assurance frameworks using MATLAB/Simulink and Python.
\end{rSubsection}

\end{rSection}


\end{document}
